SPIRAL OPTIMIZATION ALGORITHM

### 2021-10-17 Semester I/Analisis Numerik Lanjut/Tugas Kerang/spiral.Rmd
new graf

@@

xxxxx

>>>>

# untuk sistem persamaan
ikanx_2 = function(f,a,b){
  x = seq(a,b,by = .25)

  temp_plot =
    expand.grid(x,x) %>%
    rename(x = Var1,
           y = Var2) %>%
    mutate(z = f(x,y)) %>%
    filter(round(z,3) == 0)

  return(temp_plot)
}

@@

```{r out.width = "75%",echo=FALSE,fig.retina=10,fig.cap = "Plot Soal 1: f1 dan f2"}
df1 = ikanx_2(f1,-10,10)
df2 = ikanx_2(f2,-10,10)

ggplot() +
  geom_point(data = df1, aes(x,y)) +
  geom_point(data = df2, aes(x,y))
```
